Step 1: import data into RStudio
```{r}
triple_df = read.csv("Documents/BUS2_194A_Statistical_Analysis/Chapter_13/Triple-A-edited.csv", header = TRUE, colClasses = c("factor","factor", "numeric"))
summary(triple_df) #summary statistic 
```
interpretation: the categorical variable (Team Name's Division North, South, and West) has 6, 4, and 4 observations, respectively. The quantitative
#variable Attendance has a numeric summary with mean = 7300 and median = 7471. The average attendance for the 3 divisions is 7300. 

Step 2: data visualization using boxplot (Note: you can explore dotplots, histogram, etc)
```{r}
boxplot(Attendance ~ Division, data = triple_df, main = "Attenance among 14 teams for the 3 divisions analysis", xlab = "Divisions", ylab = "Attendance")
```
interpretation: the boxplot gives us a visual summary of the data. It shows the median, outliers, quartiles, maximum and minumum values. It is observed from the plot that the median values of all three divisions (7800, 5400, 8400) are different. We can visually see the variation in the data from the boxplot, which shows high-within group variance and high among group-variance. 
additional interpretation: we see that not all the notches in the boxplots overlap and we can conclude that with 95% confidence, that the true medians 
#do differ. 

#Step 3: ANOVA test 
```{r}
triple_anova = aov(Attendance ~ Division, data = triple_df) 
summary(triple_anova)
```
interpretation: 
- the variance (MSE) is 1301393 
- the p-value is less than 0.05, so we reject the null hypothesis 

Step 4: conclusion: We can conclude that there are significant differences between the mean attendance among the 3 divisions 

Step 5: assumption test

the first assumption is to check for the homogeneity of variance (i.e., are the pop.variance the same)
graphical analysis to check for variance using the Residuals vs Fitted plot 
plot(triple_anova, 1)
interpretation: points 8, 3, and 6 are detected as outliers, which can severely affect the normality and variance assumptions. It can be useful to remove outliers from the data to meet the test assumptions.

We can use a test called the Levene's test to check for variance 
```{r}
library(car)
test = leveneTest(Attendance ~ Division, data = triple_df)  #test for variance 
test
```
interpretation: from the output we can see that the p-value is not less than the significant level of 0.05, this means that there is no evidence to suggest that the variance across methods is significantly different. Therefore, we can assume the homogeneity of variances in the different division groups 

the second assumption is to check for normality (i.e. is our dataset normally distributed)
the normal probability plot of residuals (Normal Quantile plot) is used to check for normality
the points on the plot should approximately follow a straight line 
plot(triple_anova, 2)
interpretation: the points on the plot do not really follow a straight line, so we cannot assume normality, we may have to perform another test to confirm normality 

the Shapiro-Wilk test on the ANOVA residuals is used to confirm normality
extract the residuals 
triple_residuals = residuals(object = triple_anova)
run Shapiro-Wilk test 
shapiro.test(x = triple_residuals)
interpretation: W = 0.95, p-value = 0.5 which indicates that the normality assumption is not violated because p-value is greater than 0.05 

Report part 3 
multiple comparison procedure using t test 
```{r}
pairwise.t.test(triple_df$Attendance, triple_df$Division, p.adj = "bonf") #bonf means bonferroni
```

another method for multiple comparison is Tukey's Honest Significant Differences (HSD)
```{r}
TukeyHSD(triple_anova, p.adj = "bonf")
```

#interpretation North: with an alpha value of 0.05 (p-value = 0.6 > 0.05), we FTR Ho
#the population mean attendance for division North is equal to the population mean attendance for division West 

#interpretation B: with an alpha value of 0.05 (p-value = 0.012 < 0.05), we can reject Ho, the population mean attendance for division South is not equal to division West 

#overall interpretation: in effect, our conclusion is that the population mean attendance for division South differs from West but it is the same among North and West 


